The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Center table headers
find -> found

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand{\xmark}{\sffamily x}

@@

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we find that this most accurately represents both the maturity and activity of the projects. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\newcommand{\xmark}{\sffamily x}
\newcommand{\tblhead}[1]{\multicolumn{1}{| c |}{\textbf{#1}}}

@@

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represents both the maturity and activity of the projects. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.
